---
title: "p8105_hw1_jl5934"
author: "Jesus Luevano"
date: "2023-09-15"
output: github_document
---

```{r setup, echo = FALSE, results = hide}
library("moderndive")
library(tibble)
library(ggplot2)
library(tibble)
library(tidyverse)

data("early_january_weather")
```

# Problem 1

## Describing the Dataset

The variables of the dataset are `r names(early_january_weather)`.

The size of the dataset is `r nrow(early_january_weather)` rows by `r ncol(early_january_weather)` columns.

The mean temperature of the 385 observations in the dataset is `r mean(early_january_weather$temp)` degrees Celsius. 

```{r scatterplot}
scatter_df <- tibble(
  x = early_january_weather$time_hour,
  y = early_january_weather$temp
) 

ggplot(scatter_df, aes(x = x, y = y, color = early_january_weather$humid)) + geom_point()
```

```{r output plot}
ggsave("scatterplot_problem1.pdf", height = 4, width = 6)
```


# Problem 2

## Constructing the dataframe

```{r}
df_2 = tibble(
  norm_sample = rnorm(10, mean = 1),
  norm_sample_pos = norm_sample > 0,
  char = "abcabcabca",
  factor = factor(char)
)
```

## Means of the dataframe

The mean of the random sample of normal distribution is `r`.

The mean of the logical vector is `r`.

The mean of the character vector is `r`.

The mean of the factor vector is `r`.

```{r conversion, results = hide}
as.nuermic()

as.numeric()

as.numeric()
```


