---
title: "p8105_hw1_jl5934"
author: "Jesus Luevano"
uni: "jl5934"
date: "2023-09-18"
output: github_document
---

```{r setup}
library(moderndive)
library(tidyverse)
```

# Problem 1

## Access the dataset

We will load the 'early_january_weather' dataset. 

```{r}
data("early_january_weather")
```


## Describing the Dataset

We will then run commands to evaluate the variables and some basic statistics on them.

The variables of the dataset are `r names(early_january_weather)`.

The size of the dataset is `r nrow(early_january_weather)` rows by `r ncol(early_january_weather)` columns.

The samples are all originating from the site EWR, during the month of January 2013. The days range from 1-15, suggesting they were collected the first half of the month. The samples hours from 0-23 to represent a 24 hour day.

The mean temperature of the 385 observations in the dataset is `r mean(pull(early_january_weather, temp))` degrees Celsius, with a standard deviation of `r sd(pull(early_january_weather, temp))` degrees Celsius.

In addition, the mean dew point of the dataset is `r mean(pull(early_january_weather, dewp))`, mean humidity of the dataset is `r mean(pull(early_january_weather, humid))`, mean wind speed is `r mean(pull(early_january_weather, wind_speed))`, mean precipitation is `r mean(pull(early_january_weather, precip))`, and mean visbility was `r mean(pull(early_january_weather, visib))`. 

Because there were 'NA' values in both wind gust, wind direction, and pressure, the means could not be calculated without dealing with those missing values.

## Making the scatterplot

We will make a scatterplot evaluating the temperature (C) by time hour it was collected. We will also color code by humidity.

```{r scatterplot}
scatter_df <- tibble(
  x = pull(early_january_weather, time_hour),
  y = pull(early_january_weather, temp)
) 

ggplot(scatter_df, aes(x = x, y = y, color = pull(early_january_weather, humid))) + geom_point() + 
  xlab("Hour sample taken") + ylab("Temperature (C)") + labs(title="Temperature at sample Hour", color = "Humidity")
```

Looking at the scatterplot there is a general increase in temperature as time hour it was taken increases, but it is not a pure linear relationship as it somewhat oscillates. In addition, when color-coded by humidity we see that the humidity also seems to increase with the time hour that the sample was taken.

## Saving the plot.

```{r output plot}
ggsave("scatterplot_problem1.pdf", height = 4, width = 6)
```


# Problem 2

## Constructing the dataframe

```{r}
set.seed(817)

df_2 = tibble(
  norm_sample = rnorm(10, mean = 1), 
  norm_sample_pos = norm_sample > 0,
  char = "helloworld",
  factor = factor(c("first", "second", "third", "first", "second", "third", "first", "second", "third", "first"), levels = c("first", "second", "third"))
)
```

## Means values from the dataframe

The mean of the random sample of normal distribution is `r mean(pull(df_2, norm_sample))`.

The mean of the logical vector is `r mean(pull(df_2, norm_sample_pos))`. However, this is just interpreting a binary variable so it is not a true mean.

The mean of the character vector is NA when attempted via `r mean(pull(df_2, char))`.

The mean of the factor vector is NA when attempted via `r mean(pull(df_2, factor))`.


## Changing data type

```{r conversion, eval = FALSE}
df_2$char = as.numeric(as.character(pull(df_2, char)))

df_2$factor =  as.numeric(as.factor(pull(df_2, factor)))
```

When we try to convert the character vector into a numeric one, it is unable to and coerces them all to NA. However when we attempt it with the factor level it is able to convert it to numeric, assigning values from 1-3 based on the factor level it was originally. 
