---
title: "p8105_hw1_jl5934"
author: "Jesus Luevano"
date: "2023-09-15"
output: github_document
---

```{r setup, echo = FALSE}
library(moderndive)
library(tibble)
library(ggplot2)
library(tibble)
library(tidyverse)

data("early_january_weather")
```

# Problem 1

## Describing the Dataset

The variables of the dataset are `r names(early_january_weather)`.

The size of the dataset is `r nrow(early_january_weather)` rows by `r ncol(early_january_weather)` columns.

The mean temperature of the 385 observations in the dataset is `r mean(pull(early_january_weather, temp))` degrees Celsius. 

```{r scatterplot}
scatter_df <- tibble(
  x = pull(early_january_weather, time_hour),
  y = pull(early_january_weather, temp)
) 

ggplot(scatter_df, aes(x = x, y = y, color = early_january_weather$humid)) + geom_point()
```

```{r output plot}
ggsave("scatterplot_problem1.pdf", height = 4, width = 6)
```


# Problem 2

## Constructing the dataframe

```{r}
df_2 = tibble(
  norm_sample = rnorm(10, mean = 1),
  norm_sample_pos = norm_sample > 0,
  char = "helloworld",
  factor = factor(c("first", "second", "third", "first", "second", "third", "first", "second", "third", "first"), levels = c("first", "second", "third"))
)
```

## Means of the dataframe

The mean of the random sample of normal distribution is `r mean(pull(df_2, norm_sample))`.

The mean of the logical vector is `r mean(pull(df_2, norm_sample_pos))`.

The mean of the character vector is NA when attempted via "r mean(pull(df_2, char))"

The mean of the factor vector is NA when attempted via "r mean(pull(df_2, factor))"


## Chaging data type

```{r conversion, eval = FALSE}
df_2$char = as.numeric(as.character(df_2$char))

df_2$factor =  as.numeric(as.factor(df_2$factor))
```

When we try to convert the character vector into a numeric one, it is unable to and coerces them all to NA. However when we attempt it with the factor level it is able to convert it to numeric, assigning values from 1-3 based on the factor level it was originally. 
